Javelins with hyper3 objects

### 2025-12-23 inst/javelin.Rmd
attemptstable objects

```{r,label=loadjavelinandconvert}
javelin_table <- read.table("javelin.txt",header=TRUE)
a <- javelin_table # saves typing
javelin_table
```

Above, we see that Chopra threw 87.03m on his first throw, 87.58m on
his second, and so on.  Vadlejch threw 83.98m on his first throw, etc.
We may convert this to a named vector with elements being the throw
distances, and names being the competitors, using
`attemptstable2supp3()`:

```{r,label=converttosupp3,cache=TRUE}
javelin_vector <- attemptstable2supp3(a,decreasing=TRUE,give.supp=FALSE)
javelin_vector
o <- javelin_vector # saves typing
```

@@

```{r, label=plotjav}
n <- length(levels(as.factor(names(o))))
plot(o,pch=16,col=rainbow(n)[as.factor(names(o))])
legend("topright",pch=16,col=rainbow(n),legend=levels(as.factor(names(o))))
```

Now convert the attempts table to a `hyper3` object, again using
function `attemptstable2supp3()` but this time pass `give.supp=TRUE`.
However, note that there are two reasonable interpretations: firstly,
we simply ignore no-throws [in the package docs, these are sometimes
referred to as "DNF", or "Did not finish", following Formula 1
terminology]:

```{r,label=dothething2,cache=TRUE}    	   
javelin1 <- ordervec2supp3(v=names(o)[!is.na(o)])
H1 <- javelin1 # saves typing
javelin1_maxp  <- maxp(H1)
m1 <- javelin1_maxp
```

Secondly, we may treat no-throws as being inferior to any actual
measured throw.  To do this it is easiest to pass `give.supp=TRUE` to
`attemptstable2supp3()`:

```{r,label=dothething1,cache=TRUE}    	   
javelin2 <- attemptstable2supp3(a,decreasing=TRUE,give.supp=TRUE)
H2 <- javelin2 # saves typing
javelin2_maxp <- maxp(H2)
m2 <- javelin2_maxp
```

@@

```{r,plotm}
rbind(one=m1,two=m2)
pie(m1)
pie(m2)
dotchart(m1,pch=16)
dotchart(m2,pch=16)
ordertransplot(m1,m2)
```

```{r,dothetests,cache=TRUE}
equalp.test(javelin1)
equalp.test(javelin2)
```

@@

```{r,label=savejavelindataset}
save(javelin1,javelin2,javelin_table,javelin_vector,javelin1_maxp,javelin2_maxp,  file="javelin.rda")
```

>>>>

```{r, label=loadjavelinandconvert}
javelin_table <- as.attemptstable(read.table("javelin.txt", header=TRUE))
a <- javelin_table # saves typing
javelin_table
```

Above, we see that Chopra threw 87.03m on his first throw, 87.58m on
his second, and so on.  Vadlejch threw 83.98m on his first throw, etc.
We may convert this to a named vector with elements being the throw
distances, and names being the competitors:

```{r, label=converttosupp3, cache=TRUE}
javelin_vector <- as.vector(javelin_table)
javelin_vector
o <- javelin_vector # saves typing
```

@@

```{r, label=plotjav}
n <- length(levels(as.factor(names(o))))
plot(o, pch=16, col=rainbow(n)[as.factor(names(o))])
legend("topright", pch=16, col=rainbow(n), legend=levels(as.factor(names(o))))
```

Now convert the attempts table to a `hyper3` object, using function
\code{suppfun()}.  However, note that there are two reasonable
interpretations: firstly, we simply ignore no-throws [in the package
docs, these are sometimes referred to as "DNF", or "Did not finish",
following Formula 1 terminology] and to do this we pass
`dnf.last=FALSE`:

```{r, label=dothething2, cache=TRUE}
javelin1 <- suppfun(javelin_table, dnf.last=FALSE)
H1 <- javelin1 # saves typing
javelin1_maxp  <- maxp(H1)
m1 <- javelin1_maxp
```

Secondly, we may treat no-throws as being inferior to any actual
measured throw.  We specify `dnf.last=TRUE`:

```{r,label=dothething1,cache=TRUE}    	   
javelin2 <- suppfun(javelin_table, dnf.last=TRUE)
H2 <- javelin2 # saves typing
javelin2_maxp <- maxp(H2)
m2 <- javelin2_maxp
```

@@

```{r, label=plotm}
rbind(one=m1, two=m2)
pie(m1)
pie(m2)
dotchart(m1, pch=16)
dotchart(m2, pch=16)
ordertransplot(m1, m2)
```

```{r, dothetests, cache=TRUE}
equalp.test(javelin1)
equalp.test(javelin2)
```

@@

```{r,label=savejavelindataset}
save(javelin1, javelin2, javelin_table, javelin_vector, javelin1_maxp, javelin2_maxp, file="javelin.rda")
```
